Probabilities and propensities: conversion experiences in online grocery shopping

### 2017-03-22 lists_conversion_experience.rmd
fixing references

Combinatorial surplus, however, does not exhaust what might be found in the data. The relevancy model that DunnHumby implemented for Tesco (as for so many other  businesses) seeks to balance the tensions between proliferating associations and relative closure. It responds to the problem of finding an ordering in which the propensities of things as commodities and the propensities of people mingle with each other, without overflowing  the site of their  ordering encounter, the list.[^181.1] Big data discourse in its promissory mode  attributes potency to personalization: 'most important, using big data we hope to identify specific individuals rather than groups' [@Mayer-Schönberger_2013]. As Turow and co-authors conclude in their account of transformation of retail space: 'through it all, knowingly and not, and away from the spotlights of fierce social debate, retailers are encouraging daily routines that accept data-driven personalization as a centrifugal public force' [@Turow_2015, 476].

@@

The models Patel so briefly mentioned are all classifiers, predictive models that spatially order  variables in a dataset as a high dimensional vector space. Operating in the vector space, models classify people and events. Much of the operational formation of the classifier models received scant reference in Patel's presentation. It is likely that in DunnHumby's models the classifying model at the heart of the recommender system constructs a decision boundary in vector space between points that belong to different classes of things [@Mackenzie_2015]. The classes of things are binary: `recommended` or `not recommended,` and for many of the models shown in the graph, membership of a class is expressed as a probability.  The logistic regression model generates probabilities for each product for each customer. Patel did not articulate the implication of the contrast between the left and right hand side of the graphic. Although the statistical framing appears explicitly (e.g. in measuring the precision of  recommender systems), the underlying shift to a statistical model is barely mentioned. In becoming predictive, the 'Have You Forgotten?' recommendations have included a version of the social in the form of a  model that seeks to identify relations between variables.  The relevance of recommendations pivots on the apprehension of social order by a model.

>>>>

Combinatorial surplus, however, does not exhaust what might be found in the data. The relevancy model that DunnHumby implemented for Tesco (as for so many other  businesses) seeks to balance the tensions between proliferating associations and relative closure. It responds to the problem of finding an ordering in which the propensities of things as commodities and the propensities of people mingle with each other, without overflowing  the site of their  ordering encounter, the list.[^181.1] Big data discourse in its promissory mode  attributes potency to personalization: 'most important, using big data we hope to identify specific individuals rather than groups' [@Mayer-Schonberger_2013]. As Turow and co-authors conclude in their account of transformation of retail space: 'through it all, knowingly and not, and away from the spotlights of fierce social debate, retailers are encouraging daily routines that accept data-driven personalization as a centrifugal public force' [@Turow_2015, 476].

@@

The models Patel so briefly mentioned are all classifiers, predictive models that spatially order  variables in a dataset as a high dimensional vector space. Operating in the vector space, models classify people and events. Much of the operational formation of the classifier models received scant reference in Patel's presentation. It is likely that in DunnHumby's models the classifying model at the heart of the recommender system constructs a decision boundary in vector space between points that belong to different classes of things [@Mackenzie_2015e]. The classes of things are binary: `recommended` or `not recommended,` and for many of the models shown in the graph, membership of a class is expressed as a probability.  The logistic regression model generates probabilities for each product for each customer. Patel did not articulate the implication of the contrast between the left and right hand side of the graphic. Although the statistical framing appears explicitly (e.g. in measuring the precision of  recommender systems), the underlying shift to a statistical model is barely mentioned. In becoming predictive, the 'Have You Forgotten?' recommendations have included a version of the social in the form of a  model that seeks to identify relations between variables.  The relevance of recommendations pivots on the apprehension of social order by a model.
